Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-01-30 Manuscript/manuscript.Rmd
edits

Recursive feature elimination was used to establish the optimal number of distance-type features to include in downstream analyses. It was determined that, for 10 kb resolution data, near optimal performance was obtained for models with only 32 predictors, across each resampling technique and for each cell line (Figures 9-13). Results remained consistent across the other data resolutions (Supplementary Figures 24-38). Therefore, we reduced the feature space for subsequent models to the top 32 predictors, respective to cell line, resolution, and resampling technique.

>>>>

Recursive feature elimination was used to establish the optimal number of distance-type features to include in downstream analyses. It was determined that, for 10 kb resolution data, near optimal performance was obtained for models with only 32 predictors, across each resampling technique and for each cell line (Figures 9-13). Results remained consistent across the other data resolutions (Supplementary Figures 24-38). Therefore, the feature space was reduced for subsequent models to the top 32 predictors, respective to cell line, resolution, and resampling technique.
